Computing solution space properties of combinatorial optimization problems by generic programming tensor networks

### 2022-04-19 paper/paper.tex
Updates from Overleaf

    \caption{The plot of pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lceil\gamma \times \alpha(G)\rceil$.

@@

    The ``filled'' region is caused by the fast oscillation of configuration populations of even and odd Hamming distances.

>>>>

    \caption{Pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lceil\gamma \times \alpha(G)\rceil$.

@@
